brados: declarative, programmable object storage

### 2016-05-25 paper.tex
update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

As Ceph continues to develop into a target for building distributed services
and application, it is important to not restrict use to developers seasonsed
in distributed programming and those with knowledge of intracacies of the Ceph
performance model. To this end we present Brados, a declarative language with
relational semantics for defining the behavior of RADOS object interfaces.
Brados uses a simple declarative data model and can reduce the learning curve
for new users, and allows existing developers to increase productivity by
writing less code that is more portable.

The Brados language corresponds to a subset of the Bloom language, and models the
storage system state uniformly as a collection of
relations~\cite{alvaro:cidr11}. The composition of a collection of existing
interfaces is then expressed as a collection of high-level \emph{queries} that
describe how a stream of requests (API calls) are filtered, transformed and
combined with existing state to define streams of outputs (API call returns as
well as updates to system state).  Separating the relational semantics of such
compositions from details of their physical implementations introduces a
number of degrees of freedom, similar to the ``data independence’’ offered by
database query languages.  The choice of access methods (for example, whether
to use a bytestream interface or a key/value store), storage decide
classes(e.g., whether to use HDDs or SDDs), physical layout details (e.g. a
1:1 or 1:N mapping) and execution plans (e.g.  operator ordering) can be
postponed to execution time.  The optimal choices for these physical design
details are likely to change much more often than the logical specification,
freeing the interface designer from the need to rewrite systems and device and
interface characteristics change.

@@

>>>>

As Ceph continues to develop into a target for building distributed services
and applications, it is important to not restrict use to developers seasonsed
in distributed programming and those with knowledge of the intracacies of Ceph
and its performance model. To this end we present Brados, a declarative language with
relational semantics for defining the behavior of RADOS object interfaces.
Brados uses a simple declarative data model, can reduce the learning curve
for new users, and allows existing developers to increase productivity by
writing less code that is more portable.

The Brados language corresponds to a subset of the Bloom language, and models the
storage system state uniformly as a collection of
relations~\cite{alvaro:cidr11}. The composition of a collection of existing
interfaces is then expressed as a collection of high-level \emph{queries} that
describe how a stream of requests (API calls) are filtered, transformed and
combined with existing state to define streams of outputs (API call returns as
well as updates to system state).  Separating the relational semantics of such
compositions from details of their physical implementations introduces a
number of degrees of freedom, similar to the ``data independence’’ offered by
database query languages.  The choice of access methods (for example, whether
to use a bytestream interface or a key/value store), storage device
classes (e.g., whether to use HDDs or SDDs), physical layout details (e.g. a
1:1 or N:1 mapping) and execution plans (e.g. operator ordering) can be
postponed to execution time.  The optimal choices for these physical design
details are likely to change much more often than the logical specification,
freeing the interface designer from the need to rewrite systems and device and
interface characteristics change.

@@

We now show the implementation of CORFU using Brados and use this as a vehicle
for describing additional aspects of the language of semantics.
Listing~\ref{lst:state} shows the declaration of state for the CORFU
interface. Lines 1 and 2 define the schema of the two persistent collections
that hold the current epoch value, and the log contents. These collections are
mapped onto storage within Ceph but abstract away the low-level interface
(e.g. bytestream vs key-value). Lines 5-9 define the input and output
interfaces. We use a generic schema for the input operation to simplify
how rules are defined that apply to all operation types.
